Unions of Balls and Configuration Space

### 2014-08-19 Writing/Final/article.tex
Writing Update

\begin{abstract}
Covering both the configuration space, or \emph{C-space}, and represent the right topology is hard to achieve at the same time with traditional sampling-based motion planning algorithms, such as Probabilistic Roadmap and Rapidly-Exploring Random Tree. In this paper, we proposed a method that is able to cover near optimal path and study the shape and topology of configuration space. Our method samples a serious of balls to cover the space and use the dual shape of the union of balls to re-construct space. We analysis the coverage of the space and show how these balls and their dual shape can be used to generate a graph that maintains the topology of \emph{C-space} 
\end{abstract}

\section{Introduction}
\indent\indent Planning a collision-free motion for movable object could be very challenge, especially in high dimensional space, because of the lack of knowledge to understand the shape and top of configuration space. Meanwhile, motion planning has extensive applicationsto areas like augmented reality \cite{aug}, computer-aided design \cite{design} and bioinformatics \cite{bioinformatics}. More knowledge on \emph{C-space} will be benefit to these research.

\indent Although we have seen some study in low dimensional space trying to characterize the topology of \emph{C-space} \cite{ConCompNum} \cite{interval}, these methods suffer dimension curse in high dimension space.

\indent Sampling-based method for motion planning appear to be very successful \cite{Book}. These methods are usually proved to be \emph{probabilistically complete}, thus guarantee to find a path if it exists. Medial Axis sampling \cite{MAPRM} \cite{UMAPRM} attracted researchers attention for their property of characterizing the topology of \emph{C-space} and safe clearance to obstacles, however, no structures are made of these samples to properly represent the space.

@@

\indent In this paper, we will firstly introduce sampling algorithms to cover the \emph{C-space}, medial axis sampling methods are applied to reduce the number of samples and capture the topology of the space. We then use these samples, or balls, to construct the weighted $\alpha$-shape. After simplifying the $\alpha$-shape, we will still have a simple graph, which can be used for both motion planning and topology study. We at each step, we will demonstrate algorithm results of a 2D configuration space. Some properties of our algorithm are discussed in section 4.

@@

\indent\indent In this section, we first discuss the basics of sampling-based motion planning and the method of sampling on medial axis. With the information of positions and their clearance in c-space, we have samples as spheres. We then discuss the dual shapes of the union of balls which plays an important role in understanding the shape of c-space and its topology. Some works on graph theory and topology will finally be introduced.

@@

\paragraph{A} \emph{Sampling-based Motion Planning} \hfill \\
\indent A robot is a movable object whose state can be described by $n$ parameters, or \emph{degrees of freedom} ($DOFs$). A point $<x_1, x_2, ..., x_n>$ in a n-dimensional space uniquely defines the configuration of a robot. Such space is called \emph{"Configuration Space"} or \emph{"C-space"}  ($C$). The subset of all feasible configurations is called the \emph{free space} (\emph{$C_{free}$}), while $C_{obst} = C \setminus C_{free}$ is the union of all infeasible configurations. \cite{UMAPRM} Path planning will generally be viewed as a search in a metric space $X$ for a continuous path from an initial state $x_{init}$ to a goal region $X_{goal} \subset X$. For a standard problem, $X = C$. \cite{RRT} What needs to be pointed out is that \emph{C-space} is very different from workspace which is usually formed by polygons. The shape of \emph{C-space} is usually unknown to us, unless the robot is a point.

@@

%====================================
% Sampling on medial axis
%====================================
\paragraph{B} \emph{Medial Axis Sampling} \hfill \\
\indent A simpler method that maintains the topology of \emph{C-space} but doesn't cover near optimal path is medial axis sampling. Medial Axis is also called Generallized Voronoi Diagram. The medial axis $MA(F)$ of free space $F$ is a strong deformation retract of $F$, which means $F$ can be continuously deformed onto $MA(F)$ while maintaining its topological structure. However, medial axis is hard to compute explicitly.

\indent In Figure \cite{Book}, sec. 5.6.3, Steven LaValle defined Medial Axis as "Let $(X, \rho)$ be a metric space. Let a \emph(maximal ball) be a ball $B(x,r) \subseteq X$ such that no other ball can be a proper subset the centers of all maximal balls trace out a one-dimensional set of points referred to as the \emph{medial axis}".

\indent Mapping a pair of points $A$ and $B$ in free space onto $MA(F)$, there is a path between $A$ and $B$ if and only if there is a path between their images on $MA(F)$. Such path has a very nice property of the largest clearance from obstacles.

@@

\indent The basic idea of the algorithm proposed in \cite{MAPRM} is: given a point $A$ and its nearest point on the boundary of obstacles $A'$, a ray start from $A$ with direction $\overrightarrow{A'A}$ will always intersect with $MA(F)$.

@@

\paragraph{C} \emph{Dual Shapes of Unions of Balls} \hfill\\
\indent Approximating the shape of an unknown area to study its properties is a very commonly used method. We have seen many such ideas in the study of biogeometry. As for robotics, a few people began to notice the achievements from biogeometry study and tried to apply similar methods to study the shape of \emph{C-space}. \cite{alpha intro}

@@

\indent Define a \emph{simplicial complex} $D$: a collection of simplices such that if $\bigtriangleup_T \subseteq D$ ( $\bigtriangleup_T$ is the convex hull of $T$ ), then if $U \subseteq T$, we have $\bigtriangleup_U \subseteq D$ and also that the intersection of two simplices in $D$ is either empty or another simplex in $D$. The $\alpha$-shape of a set of points $S$ is a generalization of the convex hull of those points. \cite{PathNonexistance}. H. Edelsbrunner first introduced them in \cite{PointSetShape}. By choosing different value of the one parameter $\alpha$, we can have a family of shapes with the same set of points. An example of $\alpha$-shape is in Figure \ref{fig:Alpha-shape}.

@@

%====================================
% Betti Numbers
%====================================
\paragraph{D} \emph{Betti Numbers} \hfill \\
\indent In algebraic topology, the Betti Numbers are used to distinguish topological spaces based on the connectivity of n-dimensional simplicial complexes. Informally, the \emph{n-th} Betti number ($\beta_n$) represents the rank of the \emph{n-th} homology group, which tells us the maximum number of cuts that can be mad before diving a surface into two pieces. \cite{betti wiki}

@@

\indent H. Edelsbrunner introduced a way to compute $n-th$ Betti number in \cite{Edel Book}, where he uses gaussian ellimination to compute the betti numbers with adjacency matrix.

@@

\indent \indent Traditionally, sampling based algorithms will build a graph for configuration space. These kind of graphs are proved to be able to find near optimal path, but can hardly be used to analysis the topology of paths. We want to to build a stronger representation of c-space that is both able to cover optimal path and study the topological structure of c-space. In this section, we are trying to solve the problem in 2D and answer the question "Is two paths in the same homotopy class" as a start point of using our method to study the topology of \emph{C-space}. We will first give the outline of the algorithm, and explain each step in detail.

%====================================
% Algorithm outline
%====================================
\paragraph{A} \emph{The Algorithm outline} \hfill \\
\indent Before starting introducing our algorithm, we firstly clarify some preliminary tools we can have: We are sampling in $(X, \rho)$ metric space. Let $x$ be a configuration in $X$(usually \emph{C-space}), $\rho(x)$ gives the clearance of configuration $x$. By \emph{"clearance"}, we mean its (estimated) distance to the nearest obstacles. Ball $B(x, \rho(x))$ is referred as a $"sample"$ in the rest of the section. We make no assumption of the shape of obstacles regions in \emph{C-space}.

\indent The algorithm is shown in Figure \ref{fig:Algo}. It has four phases. The first phase is to generate some random configurations in \emph{C-space}, like all other sampling-based planning algorithms do, and keep only those feasible ones. Every feasible configuration will be kept until the third phase. ($randomConfig$ keep unchanged.) In the second phase, we will sample balls centered on medial axis first and then try to cover the left area of $C_{free}$. Samples on the medial axis $MA(C_{free})$ will be used in phase three to construct the dual shape that captures the topology of $C_{free}$. After simplifying the dual shape, we will have a roadmap while maintaining the topological structure. Phase four break the topology roadmap into pieces such that no two piece can be merged without forming a loop.

\indent We will now explain each phase in detail.

@@

    // Phase Three
    \indent \State $dualShape \gets WeightedAlphaShape( some smaples )$
    \indent \State $topologyRoadmap \gets Retract(dualShape)$

@@

\indent Sampling on medial axis is well studied in \cite{MAPRM} and \cite{UMAPRM}. Besides the positions of configurations, we also keep the clearance of each configuration, thus have some balls, or samples. We also require that no new ball, when sampling, is allowed to be centered inside any existing one. For details of the algorithms, please refer to these two papers. One thing worth our notice is that using only algorithm mentioned in \cite{MAPRM}, we can get good result in narrow corridor but are more likely to ignore large open area. While using only \cite{UMAPRM} method, we can cover large open area well, but more likely to produce disconnected balls in narrow corridor. Therefore, running both algorithm is highly recommended.

\indent The reason we sample on medial axis first is that 1. these balls are maximal ones as the definition of medial axis suggests, and 2. medial axis $MA(C_{free})$ is a SDR of \emph{C-space}. \cite{MAPRM2}

\indent Figure \ref{SampleLeftArea} describes how we sample area not yet covered by balls centered on medial axis. The basic idea behind the algorithm is to keep sampling new balls on the boundary of existing ones by "pushing" random configurations inside existing balls to the boundary of them and determine if they are in any other balls. We restrict that all balls to be larger than a minimal radius ball, thus void getting a lot of very small samples.

\indent Getting configurations inside a ball doesn't have to be $O(n)$ costly. It can be done using KNN algorithm, which is more efficient than iterating everything. Since we generated random configuration $n$ times, not all are feasible, in a 2D space with area $A$. We expect to have $n/A$ configurations in an unit area. A ball with radius $r$ has area $\pi r^2$, approximately $k = \frac{n \pi r^2}{A}$ configurations are inside the ball. We then project these (uniformly distributed) configurations to the boundary of the ball. Actually, choosing a larger $k$ could be better: we virtually extend the radius of our discs, which results in a smaller density in arcs that are very close to obstacles than those far from obstacles. Samples got in this part is called \emph{regular samples}.

\indent Figure \ref{Samples} is a result of this phase running in a rectangle world with 3 obstacles in the middle. Gray balls are centered on medial axis, while green ones are not. Red points are centers.

@@

\indent One might argue that we can simply get configurations on medial and connect them as a roadmap. However, this roadmap doesn't maintain the topology of \emph{C-space}. At some corners, we will still get triangles which don't have information if there are obstacles inside the triangle. By building the dual shape, this will no longer be a problem.

\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, reconnect these retracted points with other ones using their previous connection.

@@

%====================================
% Break graph
%====================================
\paragraph{D} \emph{Breaking A Graph into Loop-free Parts} \hfill\\
\indent After getting the topology roadmap, we technically already have a planner, but still we can simplify it. We now discuss breaking a graph into several components, such that no two components can merge into a new graph without forming a loop. By doing this, a graph is even simplified. Knowing which components are the start and goal configurations in, we can find a path connecting these components immediately. This technique can be a great improve when $C-space$ is very large and traditional \emph{PRM} or \emph{RRT} methods will take a long time to solve.

\indent Let $g_1$ and $g_2$ be two graphs without loops. We say $g_1$ and $g_2$ to be mergeable if: 1. they share at least one common node, 2. the new graph formed by these two graph has no loop.

@@

%====================================
% Path topology
%====================================
\paragraph{E} \emph{Determine Paths Homotopy Class} \hfill \\
\indent A continuous function, or a map, $f: X \rightarrow Y$ is called a \emph{homotopy equivalence} if there is a map $g: X \rightarrow Y$ such that there exist a continuous function $H: X \times [0,1] \rightarrow Y$ with $H(x, 0) = f$ and $H(x,1) = g$.

@@

  \paragraph{\emph{Proof:}} 
  \indent When the number of initial random configurations approaches infinite, the boundaries of all existing balls are fully covered. So, every configuration not inside any existing balls will be samples as a ball, unless it's less than $r_{min}$ clearance.

  \begin{theorem}
  Let $B$ be the set of ball samples got in phase one. Then $|B|$ is finite.   
  \end{theorem}
  \paragraph{\emph{Proof:}} 
  \indent We restrict balls to have no less than $r_{min}$ radius and new balls to be centered outside existing ones. Assume we partition the space into $r_{min} \cdot r_{min}$ cells in 2D. The number of cells is finite, if the space is finite. Putting balls with exactly $r_{min}$ radius in the centers of these cells will cover the space totally. The number of balls is finite. Phase one will generate balls no more than the number of balls generated in this way. Figure \ref{ourdualshape} shows the dual shape of balls generated by previous phase.

@@

  $H(x) = b_i \indent, if \indent |x-b| < |x-b'|, b' \in B$

  \indent This continuous function maps any point in the space to balls centered on medial axis. Dual shape maps any points in the balls to the topology roadmap we build.

@@

  \begin{theorem}
  Let $g_1$ and $g_2$ be two loop-free graphs such that merging their common nodes will produce a new graph with loops, $\sigma_1$ and $\sigma_2$, with the same start and goal nodes, be two paths going from $g_1$ to $g_2$ via common nodes $A$ and $B$. $\sigma_1$ and $\sigma_2$ have different homotopy type if $A \neq B$
  \end{theorem}
  \paragraph{\emph{Proof}}
  \indent Because $A$ and $B$ are two common nodes shared by $g_1$ and $g_2$, if $A \neq B$, merging $g_1$ and $g_2$ will create a graph with a loop going from $A \rightarrow B \rightarrow A$. Since $\sigma_1$ and $\sigma_2$ have the same start and goal nodes, merging them will also create a loop. So $\sigma_1$ and $\sigma_2$ have different homotopy type.

>>>>

\begin{abstract}
Covering both the configuration space, or \emph{c-space}, and represent the right topology is hard to achieve at the same time with traditional sampling-based motion planning algorithms, such as Probabilistic Roadmap and Rapidly-Exploring Random Tree. In this paper, we proposed a method that is able to cover near optimal path and study the shape and topology of configuration space. Our method samples a serious of balls to cover the space and use the dual shape of the union of balls to re-construct the space. We analysis the coverage of the space and show how these balls and their dual shape can be used to generate a graph that maintains the topology of \emph{c-space}.
\end{abstract}

\section{Introduction}
\indent\indent Planning a collision-free motion for movable objects could be very challenge, especially in high dimensional space, because of the lack of knowledge to understand the shape and topology of configuration space. Meanwhile, motion planning has extensive applicationsto areas like augmented reality \cite{aug}, computer-aided design \cite{design} and bioinformatics \cite{bioinformatics}.

\indent Although we have seen some study in low dimensional space trying to characterize the topology of \emph{c-space} \cite{ConCompNum} \cite{interval}, these methods suffer dimension curse in higher dimensional space.

\indent Sampling-based methods for motion planning appear to be very successful \cite{Book}. These methods are usually proved to be \emph{probabilistically complete}, thus guarantee to find a path if it exists. Medial Axis sampling \cite{MAPRM} \cite{UMAPRM} attracted researchers attention for their property of characterizing the topology of \emph{C-space} and safe clearance to obstacles, however, no structures are made with these samples to properly represent the space.

@@

\indent In this paper, we will firstly introduce a sampling algorithm to cover the \emph{c-space}, medial axis sampling methods are applied to reduce the number of samples and capture the topology of the space. We then use these samples, or balls, to construct the weighted $\alpha$-shape. After simplifying the $\alpha$-shape, we will still have a simple graph, which can be used for both motion planning and topology study. In each step, we will demonstrate algorithm results of a 2D configuration space. Some properties of our algorithm are discussed in section 4.

@@

\indent\indent In this section, we first discuss the basics of sampling-based motion planning and the method of sampling on medial axis. With the information of positions and their clearance in c-space, we have samples as spheres, or balls. We then discuss the dual shape of the union of balls which plays an important role in understanding the shape and topology of \emph{c-space}. Some works on graph theory and topology will finally be introduced.s

@@

\paragraph{A} \emph{Sampling-based Motion Planning} \hfill \\
\indent A robot is a movable object whose state can be described by $n$ parameters, or \emph{degrees of freedom} ($DOFs$). A point $<x_1, x_2, ..., x_n>$ in a n-dimensional space uniquely defines the configuration of a robot. Such space is called \emph{"Configuration Space"} or \emph{"C-space"}  ($C$). The subset of all feasible (collision-free) configurations is called the \emph{free space} (\emph{$C_{free}$}), while $C_{obst} = C \setminus C_{free}$ is the union of all infeasible configurations. \cite{UMAPRM} Path planning will generally be viewed as a search in a metric space $X$ for continuous paths from an initial state $x_{init}$ to a goal region $X_{goal} \subset X$. For a standard problem, $X = C$. \cite{RRT} What needs to be pointed out is that \emph{C-space} is very different from workspace which is usually formed by polygons. The shape of \emph{C-space} is usually unknown to us, unless the robot is a point, in which case workspace is the \emph{C-space}.

@@

%====================================
% Sampling on medial axis
%====================================
\paragraph{B} \emph{Medial Axis Sampling} \hfill \\
\indent A simpler method that maintains the topology of \emph{C-space} but doesn't cover near optimal path is medial axis sampling. Medial Axis is also called Generallized Voronoi Diagram. The medial axis $MA(C_{free})$ of free space $C_{free}$ is a strong deformation retract of $C_{free}$, which means $C_{free}$ can be continuously deformed onto $MA(C_{free})$ while maintaining its topological structure. However, medial axis is hard to compute explicitly.

\indent In Figure \cite{Book}, sec. 5.6.3, Steven LaValle defined Medial Axis as "Let $(X, \rho)$ be a metric space. Let a \emph{maximal ball} be a ball $B(x,r) \subseteq X$ such that no other ball can be a proper subset. The centers of all maximal balls trace out a one-dimensional set of points referred to as the \emph{medial axis}".

\indent Mapping a pair of points $A$ and $B$ in free space onto $MA(C_{free})$, there is a path between $A$ and $B$ if and only if there is a path between their images on $MA(C_{free})$. Such path has a very nice property of the largest clearance from obstacles.

@@

\indent The basic idea of the algorithm proposed in \cite{MAPRM} is: given a point $A$ and its nearest point on the boundary of obstacles $A'$, a ray start from $A$ with direction $\overrightarrow{A'A}$ will always intersect with $MA(C_{free})$.

@@

\paragraph{C} \emph{Dual Shapes of Unions of Balls} \hfill\\
\indent Approximating the shape of an unknown area to study its properties is a very commonly used method. We have seen research ideas in the study of biogeometry to solve the problem. As for robotics, a few people began to notice the achievements from biogeometry study and tried to apply similar methods to study the shape of \emph{C-space}. \cite{alpha intro}

@@

\indent Define a \emph{simplicial complex} $D$: a collection of simplices such that if $\bigtriangleup_T \subseteq D$ ( $\bigtriangleup_T$ is the convex hull of $T$ ), then if $U \subseteq T$, we have $\bigtriangleup_U \subseteq D$ and also that the intersection of two simplices in $D$ is either empty or another simplex in $D$. The $\alpha$-shape of a set of points $S$ is a generalization of the convex hull of those points. \cite{PathNonexistance}. H. Edelsbrunner first introduced them in \cite{PointSetShape}. By choosing different values of the one parameter $\alpha$, we can have a family of shapes with the same set of points. An example of $\alpha$-shape is in Figure \ref{fig:Alpha-shape}.

@@

%====================================
% Betti Numbers
%====================================
\paragraph{D} \emph{Betti Numbers} \hfill \\
\indent In algebraic topology, the Betti Numbers are used to distinguish topological spaces based on the connectivity of n-dimensional simplicial complexes. Informally, the \emph{n-th} Betti number ($\beta_n$) represents the rank of the \emph{n-th} homology group, which tells us the maximum number of cuts that can be made before diving a surface into two pieces. \cite{betti wiki}

@@

\indent H. Edelsbrunner introduced a way to compute \emph{n-th} Betti number in \cite{Edel Book}, where he uses gaussian ellimination to compute the betti numbers with adjacency matrix.

@@

\indent \indent Traditionally, sampling based algorithms will build a graph for configuration space. These kind of graphs are proved to be able to find near optimal path, but can hardly be used to analysis the topology of paths. We want to to build a stronger representation of \emph{C-space} that is both able to cover optimal path and study the topological structure. In this section, we are trying to solve the problem in 2D and answer the question "Is two paths in the same homotopy class" as a start point of using our method to study the topology of \emph{C-space}. In this section, we will first give the outline of the algorithm, and explain each step in detail.

%====================================
% Algorithm outline
%====================================
\paragraph{A} \emph{The Algorithm outline} \hfill \\
\indent Before starting introducing our algorithm, we firstly clarify some preliminary tools we can have: We are sampling in $(X, \rho)$ metric space. Let $x$ be a configuration in $X$(usually \emph{C-space}), $\rho(x)$ gives the clearance of configuration $x$. By \emph{"clearance"}, we mean its (estimated) distance to the nearest obstacles. Ball $B(x, \rho(x))$ is referred to as a $"sample"$ in the rest of the section. We make no assumption of the shape of obstacles regions in \emph{C-space}.

\indent The algorithm is shown in Figure \ref{fig:Algo}. It has four phases. The first phase is to generate some random configurations in \emph{C-space}, like all other sampling-based planning algorithms do, and keep only those feasible ones. Every feasible configuration will be kept until the third phase. ($randomConfig$ keep unchanged.) In the second phase, we will sample balls centered on medial axis first and then try to cover the left area of $C_{free}$. Samples on the medial axis $MA(C_{free})$ will be used in phase three to construct the dual shape that captures the topology of $C_{free}$. After simplifying the dual shape, we will have a roadmap while maintaining the topological structure. Phase four breaks the topology roadmap into pieces such that no two piece can be merged into a new graph without forming a loop.

\indent We will now explain each phase in detail with demos.

@@

    // Phase Three
    \indent \State $dualShape \gets WeightedAlphaShape( maSmaples )$
    \indent \State $topologyRoadmap \gets Retract(dualShape)$

@@

\indent Sampling on medial axis is well studied in \cite{MAPRM} and \cite{UMAPRM}. Besides the positions of configurations, we also keep the clearance of each configuration, thus have some balls, or samples. We also require that no new ball, when sampling, is allowed to be centered inside any existing ones. For details of the algorithms, please refer to these two papers. One thing worth our notice is that using only algorithm mentioned in \cite{MAPRM}, we can get good result in narrow corridor but are more likely to ignore large open area. While using only \cite{UMAPRM} method, we can cover large open area well, but more likely to produce disconnected balls in narrow corridors. Therefore, running both algorithms is highly recommended.

\indent The reason we sample on medial axis first is that 1.these balls are maximal ones as the definition of medial axis suggests, thus may reduce the number of samples we get, and 2.medial axis $MA(C_{free})$ is a SDR of \emph{C-space}. \cite{MAPRM2}

\indent Figure \ref{SampleLeftArea} describes how we sample area not yet covered by balls centered on medial axis. The basic idea behind the algorithm is to keep sampling new balls on the boundary of existing ones by "pushing" random configurations inside existing balls to the boundary of them and determine if they are in any other balls. If not, we sample a new ball. We restrict that all balls to be larger than a minimal radius ball, thus void getting a lot of very small samples.

\indent Getting configurations inside a ball doesn't have to be $O(n)$ costly. It can be done using KNN algorithm, which is more efficient than iterating everything. Since we generated random configurations $n$ times(not all are feasible), in a 2D space with area $A$. We expect to have $n/A$ configurations in an unit area. A ball with radius $r$ has area $\pi r^2$, approximately $k = \frac{n \pi r^2}{A}$ configurations are inside the ball. We then project these (uniformly distributed) configurations to the boundary of the ball to sample new spheres. Actually, choosing a larger $k$ could be better: we virtually extend the radius of our discs, which results in a smaller density in arcs that are very close to obstacles than those far from obstacles. Samples got in this part are called \emph{regular samples}.

\indent Figure \ref{Samples} is a result of this phase running in a rectangle \emph{C-space} with 3 obstacles in the middle. Gray balls are centered on medial axis, while green ones are not. Red points are ball centers.

@@

\indent One might argue that we can simply get configurations on medial axis and connect them as a roadmap. However, this roadmap doesn't maintain the topology of \emph{C-space}. At some corners, we will still get triangles which don't have information if there are obstacles inside the triangle. By building the dual shape, this will no longer be a problem.

\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, reconnect these retracted points with other ones using their previous connection. By doing so, we got a simple graph that characterize the topology of \emph{C-space}. We would like to call it \emph{Topology Roadmap}. This roadmap can also be used to determine if paths exist between two configurations. An example of such roadmap is shown in Figure \ref{simplifiedgraph}

@@

%====================================
% Break graph
%====================================
\paragraph{D} \emph{Breaking A Graph into Loop-free Parts} \hfill\\
\indent After getting the topology roadmap, we technically already have a planner, but still we can simplify it. We now discuss breaking a graph into several components, such that no two components can merge into a new graph without forming a loop. By doing this, a graph is even simplified. Knowing which components are the start and goal configurations in, we can find a path connecting these components immediately. This technique can be a great improve when \emph{C-space} is very large and traditional \emph{PRM} or \emph{RRT} methods will take a long time to solve.

\indent Let $g_1$ and $g_2$ be two graphs without loops. We say $g_1$ and $g_2$ to be \emph{mergeable} if: 1. they share at least one common node, 2. the new graph formed by these two graph has no loop.

@@

%====================================
% Path topology
%====================================
\paragraph{E} \emph{Determine Paths in the Same Homotopy Class} \hfill \\
\indent A continuous function, or a map, $f: X \rightarrow Y$ is called a \emph{homotopy equivalence} if there is a map $g: X \rightarrow Y$ such that there exist a continuous function $H: X \times [0,1] \rightarrow Y$ with $H(x, 0) = f$ and $H(x,1) = g$.

@@

  \paragraph{\emph{Proof:}} 
  \indent When the number of initial random configurations approaches infinite, the boundaries of all existing balls are fully covered. So, every configuration not inside any existing balls will be sampled as a ball, unless it's less than $r_{min}$ clearance.

  \begin{theorem}
  Let $B$ be the set of ball samples got in phase one. Then $|B|$ is finite.   
  \end{theorem}
  \paragraph{\emph{Proof:}} 
  \indent We restrict balls to have no less than $r_{min}$ radius and new balls to be centered outside existing ones. Assume we partition the space into $r_{min} \times r_{min}$ cells in 2D. The number of cells is finite, if the space is finite. Putting balls with exactly $r_{min}$ radius in the centers of these cells will cover the space totally. The number of balls is finite. Phase one will generate balls no more than the number of balls generated in this way. Figure \ref{ourdualshape} shows the dual shape of balls generated by previous phase.

@@

  $H(x) = b_i \indent, if \indent |x-b| \leq |x-b'|, b' \in B$

  \indent This continuous function maps any points in the space to balls centered on medial axis. While every point in the balls is mapped to the dual shape form by filled triangles, nodes and edges. Filled triangles are mapped to single nodes.

@@

  \begin{theorem}
  Let $g_1$ and $g_2$ be two loop-free graphs such that merging their common nodes will produce a new graph with loops. Let $\sigma_1$ and $\sigma_2$, with the same start and goal nodes, be two paths going from $g_1$ to $g_2$ via common nodes $A$ and $B$. $\sigma_1$ and $\sigma_2$ have different homotopy type if $A \neq B$
  \end{theorem}
  \paragraph{\emph{Proof}}
  \indent Let start and goal nodes be $S$ and $E$. Because $A$ and $B$ are two common nodes shared by $g_1$ and $g_2$, if $A \neq B$, merging $g_1$ and $g_2$ will create a graph with a loop going from $S \rightarrow A \rightarrow E \rightarrow B \rightarrow S$. The path in the upper of the loop and the path in the lower have different homotopy type. Since $\sigma_1$ and $\sigma_2$ have the same start and goal nodes, merging them will create a loop. So $\sigma_1$ and $\sigma_2$ have different homotopy type.
